On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-04 tt_theorem.tex
12/4 after lunch

\begin{theorem}[Tunnel Troll Theorem]
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. The following statements hold.
\begin{enumerate}
\item At arity $\alpha \geq 3$, if $S[i] = t$ (i.e. the tunnel that stabilizes $w[i]$ is not singular) and $S[i+1] \neq \blacksquare$, then $\#bc(C_{i-1}) > \#bc(C_i)$.
\item At arity $\alpha = 2$, if $n$ is the number of $bt$ in $S[i..j]$ for some $i,j$ such that $S[i] = b$ and $i < j$, then $\#bc(C_{i-2}) - \#bc(C_{j}) \geq n$.
\end{enumerate}
\end{theorem}

@@

\begin{lemma}
\label{TTT_tunnelC_lemma}
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
If $S[i+2] = t_a$, the following statements hold.
\begin{enumerate}
\item If $S[i] = b$, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
\item If $S[i] \in \{t_s, t_o \}$, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
\item If $S[i] = t_a$, $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
\end{enumerate}
%If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ and $S[i+2] = t_a$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $S[i+l+2] = t_a$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
\end{lemma}

@@

          \node[below left] at (180:1) {$w[h-1]$};
          \node[above] at (0:0) {$w[h]$};
          \node[below] at (-120:1) {$w[h+1]$};

@@

@@

\begin{figure}
  \centering
    \begin{tabular}{cc}

      \begin{minipage}{0.48\hsize}
      \centering
        \begin{tikzpicture}

          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];

          \foreach \theta in {60,-60,120,-120,180}{
            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
          }

          \fill[blue](0:1) circle [radius=0.05];
          \draw[->, blue] (0:0.1)--(0:0.9);

          \node[below] at (-60:1) {$n_4$};

          \begin{scope}[shift=(0:2)]
            \fill[blue](0,0) circle [radius=0.05];

            \foreach \theta in {120,60,-60,0}{
             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }

            \draw[->, blue] (180:0.9)--(180:0.1);
            \draw[->, blue] (-120:0.1)--(-120:0.9);

            \node[below] at (180:1) {$w_{[h-1]}$};
            \node[above] at (0:0) {$w_{[h]}$};
            \node[below] at (-120:1) {$w_{[h+1]}$};

            \node[above] at (120:1) {$n_3$};
            \node[above] at (60:1) {$n_2$};
            \node[right] at (0:1) {$n_1$};

            \begin{scope}[shift=(-120:1)]
              \fill[blue](0,0) circle [radius=0.05];
              \foreach \theta in {-120,-60}{
                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
              }

              \node[right] at (-120:1) {$n_5$};
              \node[right] at (-60:1) {$n_6$};
            \end{scope}

          \end{scope}

          \node at (1.2,-2.5) {Pattern 1};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.48\hsize}
      \centering
        \begin{tikzpicture}

          \fill(0,0) circle [radius=0.1];

          \foreach \theta in {60,0,120,-120,180}{
            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
          }

          \draw[->, blue] (-60:0.1)--(-60:0.9);

          \begin{scope}[shift=(-60:1),shift=(0:1)]
            \fill[blue](0,0) circle [radius=0.05];
            \fill[blue](180:1) circle [radius=0.05];

            \foreach \theta in {120,60,0,-60}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }

            \draw[->, blue] (180:0.9)--(180:0.1);
            \draw[->, blue] (-120:0.1)--(-120:0.9);

            \node[below] at (180:1) {$w_{[h-1]}$};
            \node[above] at (0:0) {$w_{[h]}$};
            \node[below] at (-120:1) {$w_{[h+1]}$};

            \node[above right] at (120:1) {$n_3$};
            \node[right] at (60:1) {$n_2$};
            \node[right] at (0:1) {$n_1$};

            \begin{scope}[shift=(-120:1)]
              \fill(0,0) circle [radius=0.05];
              \foreach \theta in {180,-120,-60}{
                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
              }

              \node[left] at (180:1) {$n_4$};
              \node[right] at (-120:1) {$n_5$};
              \node[right] at (-60:1) {$n_6$};
            \end{scope}

          \end{scope}

          \node at (1.25,-4) {Pattern 2};
        \end{tikzpicture}
      \end{minipage}

    \end{tabular}
    \caption{Case of $S[h-1..h+1] = tbt$}
    \label{TTT_tunnelC_enter_usingTunnel}
\end{figure}

@@

\proof{Proof of Tunnel Troll Theorem}
%Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, 
%then it has at most one free neighbor, and hence its successor it to be stabilized there.
%Moreover, if a bead is stabilized outside a tunnel, then its position is either an entrance of a tunnel or not.
%
%Tunnel sections have three possible shapes up to symmetry : straight($S$), obtuse($O$) and acute($A$) turn (Fig. \ref{fig:TTT_tunnel}), and we will consider each of those.

@@

@@

Next, we consider the case of $\delta = 2, \alpha = 1$. We assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and $S[i+2] \in \{ t_s, t_o \} $.
Then, all $S[i+1..j]$ do not contain $t_o$; otherwise $S[i+1..j]$ contain $\blacksquare$.
Therefore according to Lemma~\ref{TTT_entrance_Tab}, $\#bc(C_{i-1}) > \#bc(C_{i})$ and moreover that, according to Lemma~\ref{TTT_exit}, $\#bc(C_{i}) \geq \#bc(C_{j})$.

On the other hand, we assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and $S[i+2] = t_a$.

Let us consider that $w[i]$ supplies two bonds (that is, $S[i] = t$).
If $S[i] \in \{ t_s, t_o \}$, $\#bc(C_{i-2}) \geq \#bc(C_{i})$ because of Lemma~\ref{TTT_exit}.
Therefore,

if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of Lemma~\ref{TTT_exit}. Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.

\qed

@@

\begin{figure}[tb]
 \centering
    \begin{tikzpicture}
	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
      \fill[shift=(180:0)] (0,0) circle [radius=0.1];

      \draw[->] (180:0.9) -- (180:0.1);

	\node[above] at (180:1) {$w_{[i-2]}$};
	\node[below] at (180:0) {$w_{[i-1]}$};
	\node[above] at (0:1) {$n_0$};

	\foreach \theta in {0,60,-60,120,-120}{
   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
  	}
 	\node[above] at (60:1) {$n_1$};
	\node[below] at (-60:1) {$n_2$};
	\node[above] at (120:1) {$n_3$};
	\node[below] at (-120:1) {$n_4$};
    \end{tikzpicture}
    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
    \label{TTT_a4_lemma_fig}
\end{figure}

@@

\begin{proof}
Consider the moment when a bead $b$ is stabilized outside $\hexagon_O^n$ for the first time. 
See Fig.~\ref{TTT_a4_first}
There is only one bead available to stabilize $b$ there, which is $b_1$. 
In order for $b$ to avoid nondeterminism, hence, none of the beads around should not attract $b$.

@@

\begin{theorem}[$\delta = 1, \alpha = 3$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $O(n)$.
\end{theorem}

@@

\begin{theorem}[$\delta= 1, \alpha=2$]
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation.
\end{theorem}

\begin{proof}
By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities. If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$. Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities. Therefore formula \ref{TTT_only_bond} hold.

\begin{eqnarray}
  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
  \label{TTT_only_bond}
\end{eqnarray}

Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.

Let us consider the case of $v_k$ is $o$. See Fig.\ref{TTT_case_of_o}. $w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$. If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding. If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive, that is, $w[i-1]$ consumes two binding capabilities. Therefore, this case consumes binding capabilities. If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings. In addition, $w[i]$ and $w[i+1]$ consume at least one binding. Therefore this case consumes binding capabilities. Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold. Thus, in this case, oritatami system can yield infinite structures but they are only zig-zag conformation.

\begin{eqnarray}
  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
  \label{TTT_only_a}
\end{eqnarray}

\begin{eqnarray}
  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
  \label{TTT_structure}
\end{eqnarray}

\begin{figure}
  \begin{center}
    \begin{tikzpicture}

      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];

      \fill[blue](0:0) circle [radius=0.05];
      \fill[blue](0:1) circle [radius=0.05];
      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];

      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
      \draw[->, blue] (0:0.1) -- (0:0.9);
      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);

      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);

      \node[below] at (-120:1) {$w[i-2]$};
      \node[above] at (0:0) {$w[i-1]$};
      \node[below] at (0:1) {$w[i]$};
      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};

      \node[above] at (60:1) {$n_1$};
      \node[below] at (-60:1) {$n_2$};

    \end{tikzpicture}
    \caption{Case of $S[i]$}
    \label{TTT_case_of_o}
  \end{center}
\end{figure}

>>>>

\begin{theorem}[Tunnel Troll Theorem]
\label{TTT}
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. The following statements hold.
\begin{enumerate}
\item At arity $\alpha \geq 3$, if $S[i] = t$ (i.e. the tunnel that stabilizes $w[i]$ is not singular) and $S[i+1] \neq \blacksquare$, then $\#bc(C_{i-1}) > \#bc(C_i)$.
\item At arity $\alpha = 2$, if $n$ is the number of $bt$ in $S[i..j]$ for some $i,j$ such that $S[i] = b$ and $i < j$, then $\#bc(C_{i-2}) - \#bc(C_{j}) \geq n$.
\end{enumerate}
\end{theorem}

@@

@@

          \node[below left] at (180:1) {$w[i]$};
          \node[above] at (0:0) {$w[i+1]$};
          \node[below] at (-120:1) {$w[i+2]$};

@@

\begin{lemma}
\label{TTT_tunnelC_lemma}
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
If $S[i+2] = t_a$, the following statements hold.
\begin{enumerate}
\item If $w[i]$ forms at least one bond, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
\item If $w[i]$ does not consumes any bond and $S[i] \in \{t_s, t_o \}$, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
\item If $w[i]$ does not consumes any bond and $S[i] = t_a$, $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
\end{enumerate}
%If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ and $S[i+2] = t_a$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $S[i+l+2] = t_a$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
\end{lemma}

\begin{proof}
%	The bead $w[i+1]$ consumes one hand and provide nothing, that is, $\#bc(C_{i}) \geq \#bc(C_{i+1})$.
%	The bead $w[i]$ consumes bond because $S[i] = b$.
%	See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
%	The bead $w[i+2]$ is stabilized at a point of neighbors of $w[i]$.
%	If $w[i]$ consumes just one hand, $w[i]$ leaves a hand, that is, $\#bc(C_{i-1}) \geq \#bc(C_{i})$.
%	Then, $w[i+2]$ consumes $w[i]$'s hand.
%	Thus, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
%	On the other hand, if $w[i]$ forms two bonds, then even if $w[i+2]$ provides two free hands, $\#bc(C_{i-1}) - \#bc(C_{i}) = \#bc(C_{i+1}) - \#bc(C_{i+2})$.
%	Thus, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
%	This argument actually work also for the case when $w[i]$ is stabilized rather by binding.

	We consider each statements. First we prove statement 1.
	The bead $w[i+1]$ consumes one hand and provide nothing.
	If $w[i]$ forms two bonds, then even if $w[i+2]$ provides two free hands, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
	On the other hand, if it leaves a free hand, it will be used by $w[i+2]$, and hence, $w[i+2]$ does not increase the binding capability.
	Thus, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
	This argument actually work also for the case when $w[i]$ is stabilized rather by binding.

	Next we prove statement 2.
	See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
	Consider the case when $w[i]$ is stabilized by a tunnel section of type $S$ or $O$.
	As prove in Lemma~\ref{TTT_exit}, $\#bc(C_{i-2}) \geq \#bc(C_{i})$.%the increase of binding capability by $w[i-1]$ and $w[i]$ is at most 0.
	The bead $w[i]$ leaves two free hand, it will be used by $w[i+2]$, and hence, $w[i+2]$ does not increase the binding capability.
	Thus, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
	This argument actually work also for the case when $w[i]$ is stabilized rather by binding.

	Finally, we prove statement 3.
	Consider the case when $w[i]$ is stabilized by a tunnel section of type $A$ and $w[i]$ does not consumes any bond.
	Then, $w[i-2]$ must consume two bonds; otherwise $w[i-2]$'s hands is used by $w[i]$.
	The bead $w[i-1]$ consumes one hand and provide nothing.
	Thus,  $\#bc(C_{i-3}) - 1 \geq \#bc(C_{i})$.
	Moreover, the bead $w[i+1]$ consumes one hand and provide nothing and $w[i]$'s hands is used by $w[i+2]$, and hence, $w[i+2]$ does not increase the binding capability.
	Therefore, $\#bc(C_{i-3}) > \#bc(C_{i+2})$.
	This argument actually work also for the case when $w[i]$ is stabilized rather by binding.
\end{proof}

@@

%\begin{figure}
%  \centering
%    \begin{tabular}{cc}
%      
%      \begin{minipage}{0.48\hsize}
%      \centering
%        \begin{tikzpicture}
%
%          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];
%          
%          \foreach \theta in {60,-60,120,-120,180}{
%            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
%          }
%
%          \fill[blue](0:1) circle [radius=0.05];
%          \draw[->, blue] (0:0.1)--(0:0.9);
%
%          \node[below] at (-60:1) {$n_4$};
%
%          \begin{scope}[shift=(0:2)]
%            \fill[blue](0,0) circle [radius=0.05];
%
%            
%            \foreach \theta in {120,60,-60,0}{
%             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
%            }
%
%            \draw[->, blue] (180:0.9)--(180:0.1);
%            \draw[->, blue] (-120:0.1)--(-120:0.9);
%
%            \node[below] at (180:1) {$w_{[h-1]}$};
%            \node[above] at (0:0) {$w_{[h]}$};
%            \node[below] at (-120:1) {$w_{[h+1]}$};
%
%            \node[above] at (120:1) {$n_3$};
%            \node[above] at (60:1) {$n_2$};
%            \node[right] at (0:1) {$n_1$};
%
%            \begin{scope}[shift=(-120:1)]
%              \fill[blue](0,0) circle [radius=0.05];
%              \foreach \theta in {-120,-60}{
%                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
%              }
%
%              \node[right] at (-120:1) {$n_5$};
%              \node[right] at (-60:1) {$n_6$};
%            \end{scope}
%            
%          \end{scope}
%
%          \node at (1.2,-2.5) {Pattern 1};
%        \end{tikzpicture}
%      \end{minipage}
%
%      \begin{minipage}{0.48\hsize}
%      \centering
%        \begin{tikzpicture}
%
%          \fill(0,0) circle [radius=0.1];
%          
%          \foreach \theta in {60,0,120,-120,180}{
%            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
%          }
%
%          \draw[->, blue] (-60:0.1)--(-60:0.9);
%
%
%          \begin{scope}[shift=(-60:1),shift=(0:1)]
%            \fill[blue](0,0) circle [radius=0.05];
%            \fill[blue](180:1) circle [radius=0.05];
%
%            
%            \foreach \theta in {120,60,0,-60}{
%              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
%            }
%
%            \draw[->, blue] (180:0.9)--(180:0.1);
%            \draw[->, blue] (-120:0.1)--(-120:0.9);
%
%            \node[below] at (180:1) {$w_{[h-1]}$};
%            \node[above] at (0:0) {$w_{[h]}$};
%            \node[below] at (-120:1) {$w_{[h+1]}$};
%
%            \node[above right] at (120:1) {$n_3$};
%            \node[right] at (60:1) {$n_2$};
%            \node[right] at (0:1) {$n_1$};
%
%            \begin{scope}[shift=(-120:1)]
%              \fill(0,0) circle [radius=0.05];
%              \foreach \theta in {180,-120,-60}{
%                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
%              }
%
%              \node[left] at (180:1) {$n_4$};
%              \node[right] at (-120:1) {$n_5$};
%              \node[right] at (-60:1) {$n_6$};
%            \end{scope}
%            
%          \end{scope}
%
%          \node at (1.25,-4) {Pattern 2};
%        \end{tikzpicture}
%      \end{minipage}
%
%      
%      
%    \end{tabular}
%    \caption{Case of $S[h-1..h+1] = tbt$}
%    \label{TTT_tunnelC_enter_usingTunnel}
%\end{figure}

@@

%Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, 
%then it has at most one free neighbor, and hence its successor it to be stabilized there.
%Moreover, if a bead is stabilized outside a tunnel, then its position is either an entrance of a tunnel or not.
%
%Tunnel sections have three possible shapes up to symmetry : straight($S$), obtuse($O$) and acute($A$) turn (Fig. \ref{fig:TTT_tunnel}), and we will consider each of those.

@@

\proof{Proof of Tunnel Troll Theorem}

@@

Next, we consider the case of $\delta = 2, \alpha = 1$. We assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and all $S[i+2..j]$ are  $ t_s$ or  $t_o$.
According to Lemma~\ref{TTT_entrance_Tab}, $\#bc(C_{i-1}) > \#bc(C_{i})$ and moreover that, according to Lemma~\ref{TTT_exit}, $\#bc(C_{i}) \geq \#bc(C_{j})$.
Thus, binding capability of the conformation decrease per a subsequence $bt_s$ or $bt_o$.

On the other hand, we assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and there is a element of $S[i+2..j]$ such that it is $t_a$.
All $S[i+3..j]$ do not contain $t_o$; otherwise $S[i+4..j+1]$ contain $\blacksquare$.
Therefore, $S[i+2] = t_a$.
According to Lemma~\ref{TTT_exit}, on statement 1, 2, $\#bc(C_{i-2}) > \#bc(C_{i+2})$ and if $i \leq j - 3$, $\#bc(C_{i+2}) \geq \#bc(C_{j})$.
Thus, binding capability of the conformation decrease per a subsequence $bt_a$ unless $w[i]$ does not consumes any bond.
If $w[i]$ does not consumes any bond and $S[i] = t_a$, that is, $S[i-1..i+2] = bt_abt_a$, then $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
In this case, two subsequences of $bt_a$ collaborate decreasing binding capability but eventually, two subsequences decrease two bond.
That is, one subsequence decrease binding capability.

Hence, if $S[i..j]$ contain n's subsequences of $bt$, $\#bc(C_{i-2}) - \#bc(C_{j}) \geq n$
\qed

@@

%\begin{figure}[tb]
% \centering
%    \begin{tikzpicture}
%	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
%      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
%      
%      \draw[->] (180:0.9) -- (180:0.1);
%
%	\node[above] at (180:1) {$w_{[i-2]}$};
%	\node[below] at (180:0) {$w_{[i-1]}$};
%	\node[above] at (0:1) {$n_0$};
%
%	\foreach \theta in {0,60,-60,120,-120}{
%   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
%  	}
% 	\node[above] at (60:1) {$n_1$};
%	\node[below] at (-60:1) {$n_2$};
%	\node[above] at (120:1) {$n_3$};
%	\node[below] at (-120:1) {$n_4$};
%    \end{tikzpicture}
%    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
%    \label{TTT_a4_lemma_fig}
%\end{figure}

@@

\begin{proof}
Consider the moment when a bead $b$ is stabilized outside $\hexagon_O^n$ for the first time. 
See Fig.~\ref{TTT_a4_first}.
There is only one bead available to stabilize $b$ there, which is $b_1$. 
In order for $b$ to avoid nondeterminism, hence, none of the beads around should not attract $b$.

@@

\begin{theorem}[$\delta = 1, \alpha = 3$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $2n + 14$.
\end{theorem}

@@

\begin{figure}
  \begin{center}
  \begin{tabular}{c c}
  \begin{minipage}{0.48\hsize}
  \centering
    \begin{tikzpicture}
      	\fill (0,0) circle [radius=0.1];
        \fill[blue] (60:1) circle [radius=0.05];
         \fill[blue] (120:1) circle [radius=0.05];
        \fill (0:1) circle [radius=0.1];

      \draw[dashed] (180:2) -- (0:2);
      \draw[dashed, shift=(60:1)] (180:2.5) -- (0:1.5);
       \draw[dashed, shift=(60:2)] (180:3) -- (0:1);
      \draw[->, blue] (60:0.1) -- (60:0.9);
      \draw[->, blue, shift=(60:1)] (180:0.1) -- (180:0.9);

	\node[above] at (180:1) {$p_1$};
	\node[above] at (60:2) {$p_2$};
	\node[above,shift=(120:1)]at (60:1) {$p_3$};
	\node[above]at (0:1) {$p_4$};

	\draw (180:1) circle [radius=0.05];
	\draw (60:2) circle [radius=0.05];
	\draw[shift=(120:1)] (60:1) circle [radius=0.05];

	\node at (0:2.5) {$n$};
	\node[shift=(60:1)] at (0:2) {$n+1$};
	\node[shift=(60:2)] at (0:1.5) {$n+2$};

	\node[below] at (0:0) {$w[i-1]$};
	\node[above] at (60:1) {$w[i]$};
	\node[above] at (120:1) {$w[i+1]$};
	\end{tikzpicture}
    \end{minipage}

    \begin{minipage}{0.48\hsize}
    \begin{tikzpicture}
      	\fill (0,0) circle [radius=0.1];
        \fill[blue] (60:1) circle [radius=0.05];
         \fill[blue,shift=(0:1)] (60:1) circle [radius=0.05];
        \fill (0:1) circle [radius=0.1];

      \draw[dashed] (180:2) -- (0:2);
      \draw[dashed, shift=(60:1)] (180:2.5) -- (0:1.5);
       \draw[dashed, shift=(60:2)] (180:3) -- (0:1);
      \draw[->, blue] (60:0.1) -- (60:0.9);
      \draw[->, blue, shift=(60:1)] (0:0.1) -- (0:0.9);

	\node[above] at (180:1) {$p_1$};
	\node[above] at (60:2) {$p_2$};
	\node[above, shift=(120:1)]at (60:1) {$p_3$};
	\node[above]at (0:1) {$p_4$};

	\draw (180:1) circle [radius=0.05];
	\draw (60:2) circle [radius=0.05];
	\draw[shift=(120:1)] (60:1) circle [radius=0.05];

	\node at (0:2.5) {$n$};
	\node[shift=(60:1)] at (0:2) {$n+1$};
	\node[shift=(60:2)] at (0:1.5) {$n+2$};

	\node[below] at (0:0) {$w[i-1]$};
	\node[above] at (60:1) {$w[i]$};
	\node[above, shift=(0:1)] at (60:1) {$w[i+1]$};
	\end{tikzpicture}
    \end{minipage}
    \end{tabular}
    \caption{The bead $w[i]$  the first bead outside $\hexagon^n_0$: $w[i+1]$ elongated to west (left), $w[i+1]$ elongated to east (right)}
    \label{fig:ttt_d2}
  \end{center}
\end{figure}

\begin{theorem}[$\delta= 1, \alpha=2$]
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation in $w[27n^2 + 9n + 1]$.
\end{theorem}

\begin{proof}
 We assume $w[i]$ is the first bead outside $\hexagon^n_0$
 See Fig.~\ref{fig:ttt_d2}.
 If $w[i+1]$ elongated to west and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_3$; otherwise $w[i+2]$ forms two bonds.
 If $w[i+1]$ elongated to west and $w[i+2]$ is stabilized at $p_3$, $w[i+1..]$ form a zig-zag conformation.
  If $w[i+1]$ elongated to east and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_2$; otherwise $w[i+2]$ forms two bonds.
 If $w[i+1]$ elongated to east and $w[i+2]$ is stabilized at $p_2$, $w[i+1..]$ is zig-zag conformation.
 Thus, if $w[i]$ is the first bead outside $\hexagon^k_0$ for some $k \geq n$, $\#bc(C_i) > \#bc(C_{i+1})$ or $w[i+1..]$ form a zig-zag conformation.

 We assume $w[l]$ is the first bead outside $\hexagon^k_0$ and $w[m]$ is the first bead outside $\hexagon^{k+1}_0$ for some $k,l,m$ with $k<3n$. Let $s$ be a element of $S[l+1..m-1]$. If $s = b$, $s$ does not increase binding capability.
 If $s=t$, $s$ is a element of a subsequence $bt^+b$. This subsequence does not increase binding capability according to Theorem~\ref{TTT}. Thus, $\#bc(C_l) > \#bc(C_{m})$ or $w[l..]$ form a zig-zag conformation.

 The seed $\sigma$ provides at most $2n$ binding capability, that is, $\#bc(C_0) \leq 2n$.
 Thus,  if  $w[i]$ is the first bead outside $\hexagon^{3n}_0$, then this conformation has no hand without $w[i-1]$ and $w[i]$.
 Hence, $w[27n^2 + 9n + 1..]$ form a zig-zag conformation.
\end{proof}

%By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities. If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$. Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities. Therefore formula \ref{TTT_only_bond} hold.
%
%\begin{eqnarray}
%  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
%  \label{TTT_only_bond}
%\end{eqnarray}
%
%
%Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
%
%
%Let us consider the case of $v_k$ is $o$. See Fig.\ref{TTT_case_of_o}. $w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$. If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding. If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive, that is, $w[i-1]$ consumes two binding capabilities. Therefore, this case consumes binding capabilities. If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings. In addition, $w[i]$ and $w[i+1]$ consume at least one binding. Therefore this case consumes binding capabilities. Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold. Thus, in this case, oritatami system can yield infinite structures but they are only zig-zag conformation.

%
%
%\begin{eqnarray}
%  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
%  \label{TTT_only_a}
%\end{eqnarray}
%
%\begin{eqnarray}
%  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
%  \label{TTT_structure}
%\end{eqnarray}
%
%\begin{figure}
%  \begin{center}
%    \begin{tikzpicture}
%      
%      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];
%      
%      \fill[blue](0:0) circle [radius=0.05];
%      \fill[blue](0:1) circle [radius=0.05];
%      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];
%
%      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
%      \draw[->, blue] (0:0.1) -- (0:0.9);
%      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
%      
%      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
%      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);
%      
%      \node[below] at (-120:1) {$w[i-2]$};
%      \node[above] at (0:0) {$w[i-1]$};
%      \node[below] at (0:1) {$w[i]$};
%      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};
%
%      \node[above] at (60:1) {$n_1$};
%      \node[below] at (-60:1) {$n_2$};
%        
%    \end{tikzpicture}
%    \caption{Case of $S[i]$}
%    \label{TTT_case_of_o}
%  \end{center}
%\end{figure}
%
